{\fontfamily{ptm}\selectfont A Parameter Free Accelerated Proximal Gradient Method Without Restarting }

### 2024-12-16 Notebook LaTEX/Momentum Accelerations/paper3.tex
>w<, changes

        If $\alpha_0 \in (0, 1)$ (this is true by $\gamma_0 \in (0, L]$), then the entire sequence $\alpha_k \in (0, 1)$. 

@@

    \end{definition}
    \begin{remark}
        \textcolor{red}
        {
        There exists a choice of $\rho_k \in (0, 1], \mu = 0$ such that the above algorithm is equivalent to Chambolle, Dossal 2015 \cite{chambolle_convergence_2015}. 
        When $\rho_k = 1$, this becomes just FISTA \cite{beck_fast_2009}. 
        When $L > \mu > 0$, then choosing $\rho_k = 1$ yields equation 
        \begin{align*}
            L \alpha_{k + 1}^2 = (1- \alpha_{k + 1})L \alpha_k^2 + \alpha_{k + 1} \mu. 
        \end{align*}
        Here, if we assume sequence $\alpha_k$ is constant, then $\alpha_k = \sqrt{\mu/L}$ is a solution to the above iterative equation. 
        Substituting it back to the momentum form of R-WAPG, we recovers the V-FISTA algorithm, which appears as (10.7.7) in Beck's Book \cite{beck_first-order_2017}. 
        }
    \end{remark}

>>>>

        If $\alpha_0 \in (0, 1)$ which is true by $\gamma_0 \in (0, L]$, then the entire sequence $\alpha_k \in (0, 1)$. 

@@

    \end{definition}
    \begin{remark}
        \textcolor{red}
        {
        There exists a choice of $\rho_k \in (0, 1], \mu = 0$ such that the above algorithm is equivalent to Chambolle, Dossal 2015 \cite{chambolle_convergence_2015}. 
        When $\rho_k = 1$, this becomes just FISTA \cite{beck_fast_2009}. 
        When $L > \mu > 0$, then choosing $\rho_k = 1$ yields equation 
        \begin{align*}
            L \alpha_{k + 1}^2 = (1- \alpha_{k + 1})L \alpha_k^2 + \alpha_{k + 1} \mu. 
        \end{align*}
        Here, if we assume sequence $\alpha_k$ is constant, then $\alpha_k = \sqrt{\mu/L}$ is a solution to the above iterative equation. 
        Substituting it back to the momentum form of R-WAPG, we recover the V-FISTA algorithm, which appears as (10.7.7) in Beck's Book \cite{beck_first-order_2017}. 
        }
    \end{remark}
